Bayesian Detection of Bias in Peremptory Challenges Using Historical Strike Data

### 2022-12-13 analysis/paper_draft3.Rmd
revisions to intro re power prior

In turn, the inference of bias based in part on historical strike data is relevant to lawyers for deciding whether to argue a _Batson_ violation, establishing a prima facie case, and proving that bias in the particu-lar case is more likely than not (Figure \@ref(fig:batsonworkflowfig)). One challenge for incorporating historical data is the possible incompatibility between current and historical data. This incompatibility could arise due to missing data, or if attorney bias depends on certain trial-level characteristics (e.g., defendant race, charge severity).[may need fleshing out]

@@

The use of the power prior in this context allows the explicit control of the degree of incompatibility between the current and historical trial data. Specifically, lower values (closer to 0) of the power prior parameter, $\alpha$, should be selected when incompatibility is expected to be high, and higher values (closer to 1) of the power prior parameter selected when incompatibility is low. For now, the choice of alpha is placed in the hands of the user, who will need to be able to defend their choice when presenting a _Batson_ challenge before the court.

>>>>

In turn, the inference of bias based in part on historical strike data is relevant to lawyers for deciding whether to argue a _Batson_ violation, proving a prima facie case, and ultimately persuading the trial judge that bias in the particular case is more likely than not (Figure \@ref(fig:batsonworkflowfig)). One challenge for incorporating historical data is possible incompatibility between current and historical strike data for a given attorney that may arise because of missing data or because attorney bias depends on certain trial-level characteristics (e.g., defendant race, charge severity).[may need fleshing out]

@@

The use of the power prior in this context allows lawyers to explicitly control over the assumed degree of incompatibility between the current and historical trial data. Specifically, lower values (closer to 0) of the power prior parameter, $\alpha$, should be selected when incompatibility is expected to be high, and higher values (closer to 1) of the power prior parameter selected when incompatibility is low. Accordingly, the lawyer bringing the _Batson_ challenge chooses the value of $\alpha$ and must be able to explain and defend that choice as appropriately cooresponding to the likely degree of incompatibility between the current strike data and historical strike data available in the particular case.
